Formatting Instructions for NIPS 2014

### 2014-04-23 paper/paper.tex
minor bugfixes

\section{Initial Data Processing}
Our data set consists of information collected on a single stock, including instantaneous stock prices and instantaneous values of 26 parameters ($P$) known to have some affect on the price.
These values are taken at many different time stamps.
Our goal is to predict the stock price in the near future, given current values of the parameters.

First, we create labeled data to use in training our models using the following process:
We sort the data set in increasing time.
For each line, we define $\delta$, the difference in stock price after 2 minutes, to be the current stock price subtracted from the stock price that is associated with the datapoint that is closest to 2 minutes in the future.
(Note that our datapoints are roughly 50 milliseconds apart, so we can expect that the variation in distance between sets of data points will be much less than modeling error.)
We will attempt to build a model which calculates $\delta_t$ when given $P_t$, the values of the 26 parameters at time $t$.

@@

\small{
[1] Alexander, J.A. \& Mozer, M.C. (1995) Template-based algorithms
for connectionist rule extraction. In G. Tesauro, D. S. Touretzky
and T.K. Leen (eds.), {\it Advances in Neural Information Processing
Systems 7}, pp. 609-616. Cambridge, MA: MIT Press.

[2] Bower, J.M. \& Beeman, D. (1995) {\it The Book of GENESIS: Exploring
Realistic Neural Models with the GEneral NEural SImulation System.}
New York: TELOS/Springer-Verlag.

[3] Hasselmo, M.E., Schnell, E. \& Barkai, E. (1995) Dynamics of learning
and recall at excitatory recurrent synapses and cholinergic modulation
in rat hippocampal region CA3. {\it Journal of Neuroscience}
{\bf 15}(7):5249-5262.
}

>>>>

\section{Initial Data Processing}
Our data set consists of information collected on a single stock, including instantaneous stock prices and instantaneous values of 27 parameters ($P$) known to have some affect on the price.
These values are taken at many different time stamps.
Our goal is to predict the stock price in the near future, given current values of the parameters.

First, we create labeled data to use in training our models using the following process:
We sort the data set in increasing time.
For each line, we define $\delta$, the difference in stock price after 2 minutes, to be the current stock price subtracted from the stock price that is associated with the datapoint that is closest to 2 minutes in the future.
(Note that our datapoints are roughly 50 milliseconds apart, so we can expect that the variation in distance between sets of data points will be much less than modeling error.)
We will attempt to build a model which calculates $\delta_t$ when given $P_t$, the values of the 27 parameters at time $t$.

@@

\small{
}
